\usepackage{longtable}                                        
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}
\usepackage{caption} 
\captionsetup[table]{skip=3pt}  
\providecommand{\pr}[1]{\ensuremath{\Pr\left(#1\right)}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\renewcommand{\thefigure}{\arabic{table}}
\renewcommand{\thetable}{\arabic{table}}                                     

\title{AI1110 \\ Assignment 4}
\author{Sai Pradeep \\ AI21BTECH11013}
\date{\today}


\begin{document}
	% The title page
	\begin{frame}
		\titlepage
	\end{frame}
	% The table of contents
	\begin{frame}{Outline}
		\tableofcontents
	\end{frame}
	
	% The question
	\section{Question}
	\begin{frame}{EXAMPLE 2.20}
Q:-	In a group of n people,
	\begin{enumerate}[label=(\alph*)]
		\item what is the probability that two or more persons will have
		the same birthday (month and date)?
		\item  What is the probability that someone in that
		group will have birthday that matches yours? 
	\end{enumerate}
	\end{frame}
	
	% The solution
	\section{Solution}
	\begin{frame}{Solution}
		Let $X=\cbrak{0,1}$ be a random variable representing the chances about people having same birthday. Let $Y=\cbrak{0,1}$ be a random variable representing the chances that someone has birthday same as mine. 
See Table
\eqref{table:table-1} and
\eqref{table:table-2}
	 	\end{frame}
	 \begin{frame}{Events and random variables}
	\begin{table}[ht!]
		\input{../tables/table-1.tex}
		\vspace*{5pt}
		\caption{}
		\label{table:table-1}
	\end{table}
	\end{frame}
	\begin{frame}{}
		\begin{table}[ht!]
			\centering
			\input{../tables/table-2.tex}
			\caption{}
			\label{table:table-2}	
		\end{table}
	\end{frame}
\begin{frame}{Computation for part (a)}

There are $N$ = 365 equally likely ways (number of days in a year) for each person, where their birthdays fall independently.
there are $N$ ways for the first person to have a birthday, $N - 1$ ways
for the second person without matching the first person, and $N - n + 1$ ways for the last person to have non matching birthday.	
	\end{frame}
	\begin{frame}
So there are $N(N -1) ... (N -n + 1)$ favourable outcomes.
For $n$ persons, there are $N^n$ possible outcomes.
\begin{equation*}
\pr{X=0} &= \frac{\prod_{i=0}^{n-1} (N-{i})}{N^n}
         &=\prod_{i=0}^{n-1} (1-\dfrac{i}{N})
\end{equation*}
Hence,
\begin{equation*}
	\pr{X=1} &=1-\prod_{i=0}^{n-1} (1-\dfrac{i}{365})
\end{equation*}
	\end{frame}
	%conclusion
	\begin{frame}{Computation for part (b)}
There are $N$ - 1 unfavorable days among N
days for each person to not have same birthday as mine. probability that a person does not have same birthday as mine is $\dfrac{N - 1}{N}$. For a group of n persons,
\begin{equation*}
	\pr{Y=1} &=(\dfrac{N-1}{N})^n
	         &=(1-\dfrac{1}{N})^n
\end{equation*}.
Hence,          
\begin{equation*}
	\pr{Y=0} &=1-(1-\dfrac{1}{365})^n
\end{equation*}
\end{frame}
\end{document}
